---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, results='asis'}
envreportutils::devex_badge("exploration")
```

---

# Analysis of land designations that contribute to conservation

This repository contains R code that calculates summaries of the amount of land 
designated in B.C. that contributes to conservation. It supports this 
[Environmental Reporting BC indicator]().

## Usage

### R packages required:

Other than `bcmaps`*, all required packages are available from CRAN

- rgdal
- sp
- rgeos
- raster
- maptools
- bcmaps *(install with `devtools::install_github("bcgov/bcmaps")`)
- geojsonio
- rmapshaper
- feather
- readr
- dplyr
- tidyr
- ggplot2
- ggpolypath

### Data

Input data is obtained by running the python script [here](https://github.com/bcgov/designatedlands) using the following commands:
  
```
python designatedlands.py load

python designatedlands.py process

python designatedlands.py dump --out_file=designatedlands.gpkg --aggregate_fields="category,designation"

## Download the Biogeoclimatic Zone layer from here: 
## https://catalogue.data.gov.bc.ca/dataset/biogeoclimatic-ecosystem-classification-bec-map
## and store it in your working directory

python designatedlands.py overlay BEC_BIOGEOCLIMATIC_POLY.gdb --in_layer=WHSE_FOREST_VEGETATION_BEC_BIOGEOCLIMATIC_POLY_polygon --dump_file --out_file=lands_bec.gpkg --new_layer_name=bec --aggregate_fields="bc_boundary,designation,category,zone,subzone,variant,phase,map_label"

## Download the Ecosection layer from here: 
## https://catalogue.data.gov.bc.ca/dataset/ecosections-ecoregion-ecosystem-classification-of-british-columbia
## and store it in your working directory

python designatedlands.py overlay ERC_ECOSECTIONS_SP.gdb --in_layer=WHSE_TERRESTRIAL_ECOLOGY_ERC_ECOSECTIONS_SP_polygon --dump_file --out_file=lands_eco.gpkg --new_layer_name=eco --aggregate_fields="bc_boundary,designation,category,parent_ecoregion_code,ecosection_code,ecosection_name"

```
The outputs from that script should be:

- `designatedlands.gpkg` - the land designations layer
- `lands_bec.gpkg` - the land designations layer intersected with BEC (using the `overlay` command in the conservationlands tool)
- `lands_eco.gpkg`- the land designations layer intersected with ecosections (using the `overlay` command in the conservationlands tool)

Place these in the `data` folder of this repository. You will also require `BEC_BIOGEOCLIMATIC_POLY.gdb` from [here](https://catalogue.data.gov.bc.ca/dataset/biogeoclimatic-ecosystem-classification-bec-map) and 
`ERC_ECOSECTIONS_SP.gdb` from [here](https://catalogue.data.gov.bc.ca/dataset/ecosections-ecoregion-ecosystem-classification-of-british-columbia)

The [`data-raw`](data-raw) folder contains a file [`sources.csv`](data-raw/sources.csv) that lists all of the source
land designation layers used in the analysis.

### Running the analysis

- Run the `01_clean.R` file to prepare the data. Note that this will take a long time (several hours)
- Run the `02_analysis.R` file to calculate the summaries. 
- Summary csv files are copied to the `out` directory, and summary objects for use
in the [land designations Shiny app](https://github.com/bcgov/land-designations-shinyapp)
are copied to the `out-shiny` directory.
- The `output.R` file will copy the files from `out-shiny` to the 
`../land-designations-shinyapp/app/data` folder, assuming the folder exists in 
same parent directory as this repository

## Pathway to open source

Once the data are available, this repo will be moved to the bcgov org and 
developed in the open.

## Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov-c/land-designations-indicator/issues/).

## How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). 
By participating in this project you agree to abide by its terms.

## License

    Copyright 2016 Province of British Columbia

    Licensed under the Apache License, Version 2.0 (the "License");
    you may not use this file except in compliance with the License.
    You may obtain a copy of the License at 

       http://www.apache.org/licenses/LICENSE-2.0

    Unless required by applicable law or agreed to in writing, software
    distributed under the License is distributed on an "AS IS" BASIS,
    WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
    See the License for the specific language governing permissions and
    limitations under the License.
    
This repository is maintained by [Environmental Reporting BC](http://www2.gov.bc.ca/gov/content?id=FF80E0B985F245CEA62808414D78C41B). Click [here](https://github.com/bcgov/EnvReportBC-RepoList) for a complete list of our repositories on GitHub.

