---
topic: "land"
title: "Land Designations that Contribute to Conservation in B.C."
output: envreportbc::print_ver
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE, 
                      error=FALSE)

library(ggplot2)
library(ggpolypath)
library(envreportutils) #theme_soe_facet
library(magrittr) # %>%
library(feather) #read in feather file
library(ggthemes)
library(knitr) #for knitting to PDF

## Find the root of the project so we can find the files in the directory tree.
root <- rprojroot::is_rstudio_project

read_chunk(root$find_file("03_output_static.R"))

## read in datafiles
ld_df <- read_feather(root$find_file("out-shiny/gg_ld_ecoreg.feather"))
bc_map <-  read_feather(root$find_file("out-shiny/gg_bc_bound.feather"))
bcsum <- read.csv(root$find_file("out/bc_land_designations_summary.csv"), stringsAsFactors = FALSE)
bgc <- read.csv(root$find_file("out/bc_bgc_zone_land_designations_summary.csv"), stringsAsFactors = FALSE)
eco <- read.csv(root$find_file("out/bc_ecoregions_land_designations_summary.csv"), stringsAsFactors = FALSE)
```

```{r pre}
```

Land designations that contribute to conservation are spatially-defined areas established through legislation or purchased for the protection of nature and cultural values, the conservation of biological diversity and ecosystem services and the management of natural resources. For example, conservation land designations include areas established as parks, areas identified to protect species at risk or cultural heritage, and areas that are identified to manage the balance of nature conservation and economic opportunities. This indicator reports on the status of land designations that are intended to contribute to conservation in British Columbia.


-   Land designations that contribute to conservation are summarized in
    three categories: **Protected Lands, Resource Exclusion Areas and
    Spatially Managed Areas**. The three categories span a considerable
    range in contribution to conservation, with variation in purpose,
    scope and strength---with respect to intended conservation
    outcomes---and length of the term of the designations.
-   **Protected Lands**---covering 15.4% of British Columbia---includes all
    **Parks & Protected Areas** (15.0%) and **Other Protected Lands**
    (0.4%) with the *primary* purpose of the *long-term* conservation of
    nature and cultural values.
-   **Resource Exclusion Areas**---covering 12.4% of B.C.---includes all
    designations that fully exclude one or two resource activities for
    the purpose of conservation.
-   **Spatially Managed Areas**---currently covering 24.5% of B.C.---
    includes all spatial designations managing or limiting development
    or a resource activity for the purpose of conservation, or a spatial
    management regime in place to preserve specified elements of
    biodiversity but where activity is still allowed to occur. The
    designations within this category vary significantly in purpose and
    scope of management.
-   More detail on the land designations that contribute to conservation
    and the three categories are provided in the Details section below.


\begin{center}
\fbox{
  \begin{minipage}[c]{12cm}
  
   \begingroup\centering{\textbf{Protected Lands in British Columbia}}
   
     \endgroup
     
    \vspace{1mm}
    
    \text{\textbf{15.4\%} of lands in B.C. are protected through legally established areas designated}
    
    \text{for the \textit{primary} purpose of the \textit{long-term} conservation of nature and cultural values.}
    
        \vspace{3mm}
    
    \href{http://www.env.gov.bc.ca/soe/indicators/land/protected-lands-and-waters.html}{Learn more about Protected Lands \& Waters in B.C.}
    
  \end{minipage}
}
\end{center}

\newpage

# Map of Land Designations that Contribute to Conservation in B.C. (2017)

```{r map}
```
```{r, fig.height=8, fig.width=7}
ld_map + theme(legend.position = c(0,0))
```

\newpage

# Summary of Land Designations that Contribute to Conservation in B.C. (2017)

```{r bcsummary, fig.height=8, fig.width=7}
```

\newpage

# Summary of Terrestrial Ecosystem Representation within Land Designations in B.C.

-   Ecosystems in British Columbia can be characterized as
    [biogeoclimatic zones](https://www.for.gov.bc.ca/hre/becweb/),
    geographic areas with similar patterns of energy flow, vegetation
    and soils, or as
    [ecoregions](http://www.env.gov.bc.ca/ecology/ecoregions/), areas
    with similar climate and geologic features.
-   Land designation coverage of British Columbia's 16 biogeoclimatic
    zones and 44 terrestrial ecoregions varies among and within the
    three land designation categories---Protected Lands, Resource
    Exclusion Areas and Spatially Managed Areas.

# Biogeoclimatic Zones and Land Designations that Contribute to Conservation in B.C.

```{r bgc_summary, fig.height=8.5, fig.width=8}
```

\newpage

# Ecoregions and Land Designations that Contribute to Conservation in B.C.

```{r ecoreg_summary, fig.height=8, fig.width=8}
```


\newpage

## Details of Land Designations that Contribute to Conservation 
-   **Protected Lands (15.4%)**
    -   Includes **Parks & Protected Areas (15.0%)**, designations
        enacted in legislation with a *primary* purpose of the
        *long-term* conservation of nature and cultural values *and*
        that are administered by a government parks and protected areas
        agency [BC Parks](http://www.env.gov.bc.ca/bcparks/) and [Parks
        Canada](http://www.pc.gc.ca/eng/index.aspx)). Municipal and
        regional parks and water supply areas are not included in the
        analysis at this time.
    -   Includes **Other Protected Lands (0.4%)**, such as B.C.'s
        non-governmental organization conservation areas or private
        conservation lands. These are designations and lands
        administered or owned by a [non-governmental conservation
        organization](http://ltabc.ca/publications-a-research/british-columbia-conservation-areas-summary-report-2015-16/)
        and managed for the long-term conservation of wildlife habitat
        values.
    -   Other Protected Lands also includes designations enacted in legislation with a primary
        purpose of the long-term conservation of biodiversity and/or
        ecosystem services, such as National Wildlife Areas and
        Migratory Bird Sanctuaries, both designated by the Government of
        Canada, and [Wildlife Management
        Areas](http://www.env.gov.bc.ca/fw/habitat/conservation-lands/)
        designated under the provincial [*Wildlife
        Act*](http://www.bclaws.ca/EPLibraries/bclaws_new/document/ID/freeside/00_96488_01).
-   **Resource Exclusion Areas (12.4%)**
    -   Includes designations excluding one or two resource
        activities---such as forestry, mining or large-scale
        hydro-electric development---for the purpose of conservation.
    -   The excluded resource activity is often a primary threat to
        biodiversity in the established area, making the designation an
        important contribution to conservation.
    -   Some examples include designations such as no-harvest [Wildlife
        Habitat Areas](http://www.env.gov.bc.ca/wld/frpa/iwms/wha.html)
        designated under the [*Forest and Range Practices
        Act*](http://www.bclaws.ca/Recon/document/ID/freeside/00_02069_01),
        [Grizzly Bear Habitat (Class
        1)](https://www.for.gov.bc.ca/tasb/slrp/plan17.html)
        designated under the [*Land
        Act*](http://www.bclaws.ca/EPLibraries/bclaws_new/document/ID/freeside/00_96245_01),
        and the [Sea to Sky Wildland
        Areas](https://www.for.gov.bc.ca/tasb/slrp/plan79.html)
        designated under the [*Environment and Land Use
        Act*](http://www.bclaws.ca/EPLibraries/bclaws_new/document/ID/freeside/00_96117_01).
-   **Spatially Managed Areas (24.5%)**
    -   Includes spatial designations managing or limiting development
        or a resource activity---such as forestry, mining or large-scale
        hydro-electric development---for the purpose of conservation, or a
        spatially-defined management regime in place to preserve
        specified elements of biodiversity but where activity is still
        allowed to occur.
    -   Some examples include designations such as conditional-harvest
        [Wildlife Habitat
        Areas](http://www.env.gov.bc.ca/wld/frpa/iwms/wha.html),
        conditional-harvest [Ungulate Winter
        Range](http://www.env.gov.bc.ca/wld/frpa/uwr/index.html), and
        [Visual Quality
        Objectives](http://www2.gov.bc.ca/gov/content?id=C45131B6586243CD8A91D399B5712256)---all designated under the [*Forest and Range Practices
        Act*](http://www.bclaws.ca/Recon/document/ID/freeside/00_02069_01)---and Important Fisheries Watersheds and other [legal objectives
        established for the the Great Bear
        Rainforest](https://www.for.gov.bc.ca/tasb/slrp/plan17.html)
        under the [*Land
        Act*](http://www.bclaws.ca/EPLibraries/bclaws_new/document/ID/freeside/00_96245_01).

The complete list of included land designations, category information,
data sources, and data licence details is [available in CSV
format](https://github.com/bcgov/land-designations-indicator/blob/cleanup-release/data-raw/sources.csv). Some designations were
not included at this time due to a lack of a public, authoritative data
source. These will be added to the analysis as they become available.

## Methods

Overlaps among land designations have been accounted for in the
analysis. While B.C. does use aspatial land management tools, this
indicator only reports on *legal, spatially-defined* areas that
contribute to conservation. The analysis presents the current status of
land designations and the intended contribution to conservation---the
effectiveness of land designations has not been evaluated. The [**Python**](https://www.python.org/) and [**R**](http://www.r-project.org) code for repeating the analysis and data visualizations presented on this page is available on [GitHub](https://github.com/bcgov/land-designations-indicator).


## References and Other Useful Links

-   [Learn more about Protected Lands & Waters in
    B.C.](http://www.env.gov.bc.ca/soe/indicators/land/protected-lands-and-waters.html)
-   [BC Parks](http://www.env.gov.bc.ca/bcparks/)
-   [B.C. Government Conservation
    Lands](http://www.env.gov.bc.ca/fw/habitat/conservation-lands/)
-   [British Columbia Non-Governmental Organization Conservation Areas
    Summary Report
    2015-2016](http://ltabc.ca/publications-a-research/british-columbia-conservation-areas-summary-report-2015-16/)
-   [B.C. Crown
    Land](http://www2.gov.bc.ca/gov/content?id=63DF75221AF440A4AA6A9BCD34711A8C)

## Data

\*By accessing these datasets, you agree to the licence associated with each file, as indicated in parentheses below.

-   [Indicator data: Spatial and Tabular Summaries of Land Designations
    that Contribute to Conservation in
    B.C.](https://catalogue.data.gov.bc.ca/dataset/3eedf0da-0c1d-4917-aff5-1eb8f59736bc) (Licence: [Open Government Licence - British Columbia](http://www2.gov.bc.ca/gov/content?id=A519A56BC2BF44E4A008B33FCF527F61))
-   [Ecoregions - Ecoregion Ecosystem Classification of British
    Columbia](https://catalogue.data.gov.bc.ca/dataset/d00389e0-66da-4895-bd56-39a0dd64aa78) (Licence: [Open Government Licence - British Columbia](http://www2.gov.bc.ca/gov/content?id=A519A56BC2BF44E4A008B33FCF527F61))
-   [Biogeoclimatic Ecosystem Classification (BEC)
    Map](https://catalogue.data.gov.bc.ca/dataset/f358a53b-ffde-4830-a325-a5a03ff672c3) (Licence: [Open Government Licence - British Columbia](http://www2.gov.bc.ca/gov/content?id=A519A56BC2BF44E4A008B33FCF527F61))

Published and Available On-Line at Environmental Reporting BC (November 2017):
[http://www.env.gov.bc.ca/soe/indicators/land/land-designations.html](http://www.env.gov.bc.ca/soe/indicators/land/land-designations.html)

Email correspondence to: envreportbc@gov.bc.ca
