---
topic: "land"
title: "Land Designations that Contribute to Conservation in B.C."
output: envreportbc::print_ver
---


```{r set-options, echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(echo=FALSE, cache=TRUE, message=FALSE, warning=FALSE, 
                      error=FALSE)

library(ggplot2)
library(ggpolypath)
library(envreportutils) #theme_soe_facet
library(magrittr) # %>%
library(feather) #read in feather file
library(ggthemes)
library(knitr) #for knitting to PDF

## Find the root of the project so we can find the files in the directory tree.
root <- rprojroot::is_rstudio_project

read_chunk(root$find_file("output.R"))

## read in datafiles
ld_df <- read_feather(root$find_file("out-shiny/gg_ld_ecoreg.feather"))
bc_map <-  read_feather(root$find_file("out-shiny/gg_bc_bound.feather"))
bcsum <- read.csv(root$find_file("out/bc_land_designations_summary.csv"), stringsAsFactors = FALSE)
bgc <- read.csv(root$find_file("out/bc_bgc_zone_land_designations_summary.csv"), stringsAsFactors = FALSE)
eco <- read.csv(root$find_file("out/bc_ecoregions_land_designations_summary.csv"), stringsAsFactors = FALSE)
```

```{r pre}
```

Land designations that contribute to conservation are spatially-defined areas established through legislation or purchased for the protection of nature and cultural values, the conservation of biological diversity and ecosystem services and the management of natural resources. For example, conservation land designations include areas established as parks, areas identified to protect species at risk or cultural heritage, and areas that are identified to manage the balance of nature conservation and economic opportunities. This indicator reports on the status of land designations that are intended to contribute to conservation in British Columbia.


-   Land designations that contribute to conservation are summarized in
    three categories: **Protected Lands, Resource Exclusion Areas and
    Spatially Managed Areas**. The three categories span a considerable
    range in contribution to conservation, with variation in purpose,
    scope and strength---with respect to intended conservation
    outcomes---and length of the term of the designations.
-   **Protected Lands**---covering 15.4% of British Columbia---includes all
    **Parks & Protected Areas** (15.0%) and **Other Protected Lands**
    (0.4%) with the *primary* purpose of the *long-term* conservation of
    nature and cultural values.
-   **Resource Exclusion Areas**---covering 12.4% of B.C.---includes all
    designations that fully exclude one or two resource activities for
    the purpose of conservation.
-   **Spatially Managed Areas**---currently covering 24.5% of B.C.---
    includes all spatial designations managing or limiting development
    or a resource activity for the purpose of conservation, or a spatial
    management regime in place to preserve specified elements of
    biodiversity but where activity is still allowed to occur. The
    designations within this category vary significantly in purpose and
    scope of management.
-   More detail on the land designations that contribute to conservation
    and the three categories are provided [below](#details).


\begin{center}
\fbox{
  \begin{minipage}[c]{12cm}
  
   \begingroup\centering{\textbf{Protected Lands in British Columbia}}
   
     \endgroup
     
    \vspace{1mm}
    
    \text{\textbf{15.4\%} of lands in B.C. are protected through legally established areas designated}
    
    \text{for the \textit{primary} purpose of the \textit{long-term} conservation of nature and cultural values.}
    
        \vspace{3mm}
    
    \href{http://www.env.gov.bc.ca/soe/indicators/land/protected-lands-and-waters.html}{Learn more about Protected Lands \& Waters in B.C.}
    
  \end{minipage}
}
\end{center}

\newpage

# Map of Land Designations that Contribute to Conservation in B.C. (2017)

```{r map}
```
```{r fig.height=8, fig.width=7}
ld_map + guides(fill = "legend")
```

\newpage

# Summary of Land Designations that Contribute to Conservation in B.C. (2017)

```{r bcsummary, fig.height=8, fig.width=7}
```

\newpage

```{r bgc_summary, fig.height=8, fig.width=7}
```

```{r ecoreg_summary, fig.height=8, fig.width=7}
```

## References and Other Useful Links

* Link 1
* Link 2

## Data

\*By accessing these datasets, you agree to the licence associated with each file, as indicated in parentheses below.

* Data 1
* Data 2

Published and Available On-Line at Environmental Reporting BC (September 2017):
[](http://wwwd.env.gov.bc.ca/soe/indicators/land/land-designations.html)

Email correspondence to: envreportbc@gov.bc.ca
